EcoConsPreReg

### 2020-05-25 index.Rmd
Add image to manuscript, add shiny app design info

@@

As Pu et al. (2019) identify, a designer's intention for preregistration and users' purposes for preregistration may be in conflict and undermine the overarching goal of preregistration --- to improve the reliability of scientific findings. In order to bridge this mismatch, we have taken a user-centred design approach to the problem of preregistration. We do this in two ways, by first using a series of structured and collaborative activities in a workshop setting to reflect on our own research experiences in order to capture scientific workflows as they are done in practice. And secondly to, use a real-world research problem as a case-study to test and evaluate the templates for utility and feasibility in practice.

The workshop activities aimed to help us:

@@

\*\*

@@

@@

*\<div style="width: 960px; height: 720px; margin: 10px; position: relative;"\>\<iframe allowfullscreen frameborder="0" style="width:960px; height:720px" src="https://app.lucidchart.com/documents/embeddedchart/9c4480bc-8465-4731-83e6-d24d7d2b7818" id="K4J1KZqFLi3u"\>\</iframe\>\</div\>*

@@

In order to address tis confusion among norms, I state the expected norms that the template has been designed around here. However, I don't expect users to agree on this process. Because we have kept the template in a GitHub repository that can be *forked*, people are free to adapt the template (the items themselves) to suit whatever norm they see fit about how preregistrations should be created and used.

@@

This relates to what Pu et al. found where participants 'felt their research workflow improved by having preregistration as a "forcing function" \[...\] For example, writing down study plans ahead of time might prompt them to think more thoroughly and to anticipate flexibilities / researchers' degree of freedmen advance.' (Page 13). For reviewers 'participant reports that pregistration makes the review process "easier".'
--------------------------
# References

>>>>

But not just a pre-registration template, we take into account the iterative nature of model development

@@

As Pu et al. (2019) identify, a designer's intention for preregistration and users' purposes for preregistration may be in conflict and undermine the overarching goal of preregistration --- to improve the reliability of scientific findings. In order to avert this mismatch, we have taken a user-centred design approach to the problem of preregistration. We do this in two ways, firstly, by running a series of structured and collaborative activities in a workshop setting to reflect on our own research experiences in order to capture scientific workflows as they occur practice. And secondly to, use a real-world research problem as a case-study to test and evaluate the templates for utility and feasibility in practice.

\*\*Defining the purpose of preregistration\*\*

Pu et al's key finding:

Pu et al found that because different users ascribed different purposes to preregistration, it resulted in conflicting designs of preregistration formats, which they argue may ultimately undermine the overarching goal of preregistration: "improving the reliability of scientific findings".

We state the intended purposes of the preregistration template up front:

\*\*Acknowledging different use-cases\*\*

Pu et al:

\- norms around how people use preregistration are uncertain, and vary among users.

Our use-cases:

1\. As creators

2\. As users:

The collaborative workshop activities aimed to help us:

@@

@@

### Preregistration Items ###

This will be a box or a table with numbered items, with just the preregistration item directives or question. The help-text describing each phase or key steps in the workflow is removed, as this goes in the previous table under 'model scientific workflow'.

@@

In order to address this confusion among norms, I state the expected norms that the template has been designed around here. However, I don't expect users to agree on this process. Because we have kept the template in a GitHub repository that can be *forked*, people are free to adapt the template (the items themselves) to suit whatever norm they see fit about how preregistrations should be created and used.

![Living Preregistration Workflow](./figures/LivingPreregistration.png)

### Shiny App ###

Speak back to the the predefined use-cases, how does our proposed methodology and its template address the intended use-cases and purposes?

@@

In order to address this confusion among norms, I state the expected norms that the template has been designed around here. However, I don't expect users to agree on this process. Because we have kept the template in a GitHub repository that can be *forked*, people are free to adapt the template (the items themselves) to suit whatever norm they see fit about how preregistrations should be created and used.

@@

\- **Front-heavy research timeline:** As a way of providing better decision-making to authors. By shifting decision-making to the front. Front-heavy research process. Delays the start of analysis, but results in better decision-making, because the decision-making is more carefully reasoned. But not sure want to set this out as a 'purpose' of the template, or just have this as a section in the reflection towards the end of the manuscript (will depend on how I set up the angle, and the structure of the paper). At the moment, this is my hypothesis, is that it can improve the process, but we'd need to reflect on this. And I think we could do that at the end of the manuscript.

**DEALING WITH CONFLICTING NORMS IN CREATING & USING the PREREGISTRATION TEMPLATE**
--------------------------
# References
